Template for GTEx example on cluster

### 2017-10-05 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

}
```

@@

```
load("~/flash/dataanalysis/GTeX/EQTLzscore/gtexEQTL_zscore.rds")
setwd("~/flash/dataanalysis/GTeX/EQTLzscore/")
source("./sfawrapper.R")
source("./SFAmixwrapper.R")
Y = t(zscore)
N = dim(Y)[1]
P = dim(Y)[2]

gsfamix = SFAmix.wrapper(Y,30)
gsfa = SFA.wrapper(Y, 30)
saveRDS(gsfa, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfaGTExzscore.rds")
saveRDS(gsfamix, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfamixGTExzscore.rds")

>>>>

}

SFAmix.wrapper = function(X,K){
  N = dim(X)[1]
  P = dim(X)[2]

  write.table(X,file="dscsfamix.txt",row.names=F,col.names=F)
  print(class(X))
  print(dim(X))

  if(file.exists("SFAmixout")){
    unlink("SFAmixout", recursive= T)
  }
  system("mkdir SFAmixout")

  # ~/mvash/mvsim/SFAmix/SFAmix --nf K --y dscrsfamix.txt --out SFAmixout --sep space
  # this is run on the PPS cluster
  system(paste("~/mvash/mvsim/SFAmix/SFAmix","--nf",K,"--y","dscsfamix.txt","--out",
               "SFAmixout","--sep","space",sep=" "))

  alpha=read.table("./SFAmixout/PSI")

  if(file.info("./SFAmixout/EX")$size == 1){
    return(list(L = 0, F = 0))
  } else{
    Fhat=read.table("./SFAmixout/EX")
    lambda=read.table("./SFAmixout/LAM")
    Psi=as.vector(alpha)
    Fhat=as.matrix(Fhat)
    lambda=as.matrix(lambda)
    P=dim(lambda)[2]
    n=dim(Fhat)[1]
    return(list(L = Fhat, F = lambda))
  }

}

@@

```
load("~/flash/dataanalysis/GTeX/EQTLzscore/gtexEQTL_zscore.rds")
setwd("~/flash/dataanalysis/GTeX/EQTLzscore/")
source("./sfawrapper.R")
source("./SFAmixwrapper.R")
Y = zscore
N = dim(Y)[1]
P = dim(Y)[2]
gsfa = SFA.wrapper(Y, 26)
saveRDS(gsfa, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfaGTExzscore.rds")

gsfamix = SFAmix.wrapper(Y,30)
saveRDS(gsfamix, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfamixGTExzscore.rds")
